\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-09 doc/paper.tex
add missing \code{} wrapper commands

The model boundary conditions are defined in the \fs model file
\code{FlexibleSUSY.m}, which has to be located in the model directory
\code{models/<model>/}. To add this the user should create a
\code{FlexibleSUSY.m} in the directory \code{model_files/<model>/}.
When the \code{./createmodel} command is used Flexible SUSY will create the
FlexibleSUSY.m file from the FlexibleSUSY.m.in file found in the
directory in \code{model_files} with the name specified by the
\code{--model-file=<model-file-name>} option. If no such option is
given then it will use the directory matching the option
\code{--name=<model>}.  In either case the the FlexibleSUSY.m file
which is created is then automatically placed in the directory
\code{models/<model>/} by \fs. Note that many example model
files can already be found in \code{model_files/<model>/}.

@@

DefaultPoleMassPrecision = MediumPrecision;
HighPoleMassPrecision    = {hh, Ah, Hpm};
MediumPoleMassPrecision  = {};
LowPoleMassPrecision     = {};
\end{lstlisting}
%
The first line \code{FSModelName = "@CLASSNAME@";} will be replaced
with \code{FSModelName = "<model>";} in the generated FlexibleSUSY.m
file where \code{<model>} is given by the option \code{--name=<model>} for
command \code{./createmodel}.  So the variable \code{FSModelName} then
contains the name of the \fs model.

>>>>

The model boundary conditions are defined in the \fs model file
\code{FlexibleSUSY.m}, which has to be located in the model directory
\code{models/<model>/}. To add this the user should create a
\code{FlexibleSUSY.m.in} in the directory \code{model_files/<model>/}.
When the \code{./createmodel} command is used \fs will create the
\code{FlexibleSUSY.m} file from the \code{FlexibleSUSY.m.in} file found in the
directory in \code{model_files} with the name specified by the
\code{--model-file=<model-file-name>} option. If no such option is
given then it will use the directory matching the option
\code{--name=<model>}.  In either case the the \code{FlexibleSUSY.m} file
which is created is then automatically placed in the directory
\code{models/<model>/} by \fs. Note that many example model
files can already be found in \code{model_files/}.

@@

DefaultPoleMassPrecision = MediumPrecision;
HighPoleMassPrecision    = {hh, Ah, Hpm};
MediumPoleMassPrecision  = {};
LowPoleMassPrecision     = {};
\end{lstlisting}
%
The first line \code{FSModelName = "@CLASSNAME@";} will be replaced
with \code{FSModelName = "<model>";} in the generated \code{FlexibleSUSY.m}
file where \code{<model>} is given by the option \code{--name=<model>} for
command \code{./createmodel}.  So the variable \code{FSModelName} then
contains the name of the \fs model.
